Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
ortho
FIX equation for directivity

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
The connectomes is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link from neuron $i$ to neuron $j$.
The network inference task is set as follows :
\textit{Given the observations $(x_t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the graph $G$,
where $\mathbb{1}$ is the indicator function.}

@@

By ignoring the directivity, we systematically make a true positive and a
false positive for direct link.  Hoping to orientate
correctly the most obvious directed links, we attempt to retrieve some causal
information, i.e. the directivity of the links, by computing and stacking with
our symmetric adjacency matrix a matrix of pairwise activation heuristics.
This method computes an anti-symmetric activation score $z_{ij}$ based the
variation of fluorescence signal of a neuron $j$ due to a neuron $i$ over all
timesteps:
\[
z_{ij} = \sum_{t=1}^n \mathbb{1}(X_{t+1,j} \ge X_{t, i}) \cdot
\mathbb{1}(f_1\le X_t^i \le f_2) -  \mathbb{1}(X_{t+1,i} \ge X_{t, j}) \cdot
\mathbb{1}(f_1 \le X_t^j \le f_2)
\]
where $f_1$ and $f_2$ are parameters of the method and $I$ is the indicator
function. Prior computing $z_{ij}$ only the filter defined by Equations
\ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
used.

@@

>>>>

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
The connectomes is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link from a neuron $i$ to a neuron $j$.
The network inference task is set as follows :
\textit{Given the observations $(x_t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the graph $G$,
where $\mathbb{1}$ is the indicator function.}

@@

By ignoring the directivity, we systematically make a true positive and a
false positive for direct link.  Hoping to orientate
correctly the most obvious directed links, we attempt to retrieve some causal
information, i.e. the directivity of the links, by computing and stacking with
our symmetric adjacency matrix a matrix of pairwise activation heuristics.
This method computes an anti-symmetric activation score $Z$ based the
variation of fluorescence signal of a neuron $j$ due to a neuron $i$ over all
time steps:
\[
\hat{Z}: z_{ij} = \sum_{t=1}^{T - 1}
    \mathbb{1}(x_{t+1,j} - x_{t, i} \in \left[f1, f2 \right]) -
    \mathbb{1}(x_{t+1,i} - x_{t, j} \in \left[f1, f2 \right])
\]
where $f_1$ and $f_2$ are parameters of the method.

@@

For the directory method, only filters defined by Equations
\ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
used.
